Quantifying the ease of viral escape from broad and narrow antibodies to influenza hemagglutinin

### 2017-10-16 paper/manuscript.tex
Add a few sentences to results section 4

\begin{figure}
\centerline{\includegraphics[width=0.8\textwidth]{figs/neutralization_curves/WT_neutralization_curves.pdf}}
\caption{\label{fig:neutcurves}
{\bf Neutralization of wildtype virus by each antibody, and the fraction of virions surviving at each concentration used in our experiments.}
The curves show neutralization of wildtype A/WSN/1933 virus. 
Each point represents the mean and standard error of three measurements. 
\comment{Is the preceding sentence correct?}
The vertical dotted lines show the concentrations of antibody used in our selections, and the tables give the overall fraction of the mutant virus libraries that survived at each concentration.
}
\end{figure}

@@

\subsection*{The selected mutations are in the binding footprints for all antibodies}
We visualized for each mutation the fraction surviving selection as a logoplot, and for each site mapped the mutation with the maximum fraction surviving selection onto the HA structure, shown in Figure~\ref{fig:structures}. 
For all of the antibodies, the sites with mutations exhibiting the greatest fraction escape localize in the antibody-binding footprint.

% For S139/1, we see strong escape at three sites. These three sites were previously reported as sites of escape in selection experiments with S139/1 (cite Yoshida) G158N mutation introduces a potential glycosylation site
% The binding footprint of FI6v3 and C179 and the angle of approach of both antibodies is very similar (cite dreyfus). 
% For these two antibodies, we see selection for a few common escape mutations (S/T at site280, S at site 291, R at 47 / 48 (HA2), but also selection for distinct escape mutations (site 2, site 38, site 323, sites 42, 43)

\begin{figure}
\centerline{\includegraphics[width=\textwidth]{figs/logoplots_pymol/logoplots_pymol.pdf}}
\centerline{\includegraphics[width=0.7\textwidth]{figs/stalkAbs_zoomed/stalkAbs_zoomed.pdf}}
\caption{
\label{fig:structures}
\comment{Juhye, can you actually merge these two figures into one image.
Some of the journals (\textit{Cell Host \& Microbe}, \textit{Immunity}) limit papers to 6 figures.
The first figure can be panel (A).
Include a healthy amount of vertical space, and make the current (A) and (B) into (B) and (C).
Also, can you do the following:
(1) Put the stalk zooms inside a frame box (a thin black or grey line) -- this should make the cutting off look better.
(2) Clip the zoom boxes a little further on the right so that the zoomed sites are slightly bigger.
(3) Move the scale bar legend below the zoom panels to separate it from the color labeling of what will now be panel (A).
(4) Label the scale bar ``fraction surviving''.
(5) For the tree figure, the logo plot for that site is now shown in panel (A) of the same figure. So you can get rid of that, and just include labels that indicate that green means binding / neutralization by C179, and the letters are the amino acid at site 38.
}
}
\end{figure}

>>>>

\begin{figure}
\centerline{\includegraphics[width=0.8\textwidth]{figs/neutralization_curves/WT_neutralization_curves.pdf}}
\caption{\label{fig:neutcurves}
{\bf Neutralization of wildtype virus by each antibody, and the fraction of virions surviving at each concentration used in our experiments.}
The curves show neutralization of wildtype A/WSN/1933 virus. 
Each point represents the mean and standard deviation of three measurements. 
The vertical dotted lines show the concentrations of antibody used in our selections, and the tables give the overall fraction of the mutant virus libraries that survived at each concentration.
}
\end{figure}

@@

\subsection*{The selected mutations are in the binding footprints for all antibodies}
We visualized for each mutation the fraction surviving selection as a logoplot, and for each site mapped the mutation with the maximum fraction surviving selection onto the HA structure, shown in Figure~\ref{fig:structures}A. 
For all of the antibodies, the sites with mutations exhibiting the greatest fraction escape localize in the antibody epitope.

For S139/1, we observed strong escape mutations at sites 156, 158, and 193, in H3 numbering. 
These three sites surround the receptor-binding pocket, and were previously reported as sites of escape in selection experiments with S139/1~\citep{yoshida2009cross}.
The mutation contributing the greatest fraction of virions surviving selection, G158N, introduces a glycosylation motif (N-X-S/T).

% The binding footprint of FI6v3 and C179 and the angle of approach of both antibodies is very similar (cite dreyfus). 
% For these two antibodies, we see selection for a few common escape mutations (S/T at site280, S at site 291, R at 47 / 48 (HA2), but also selection for distinct escape mutations (site 2, site 38, site 323, sites 42, 43)

\begin{figure}
\centerline{\includegraphics[width=\textwidth]{figs/logoplots_pymol/logoplots_pymol.pdf}}
\caption{
\label{fig:structures}
\comment{Juhye, can you actually merge these two figures into one image.
Some of the journals (\textit{Cell Host \& Microbe}, \textit{Immunity}) limit papers to 6 figures.
The first figure can be panel (A).
Include a healthy amount of vertical space, and make the current (A) and (B) into (B) and (C).
Also, can you do the following:
(1) Put the stalk zooms inside a frame box (a thin black or grey line) -- this should make the cutting off look better.
(2) Clip the zoom boxes a little further on the right so that the zoomed sites are slightly bigger.
(3) Move the scale bar legend below the zoom panels to separate it from the color labeling of what will now be panel (A).
(4) Label the scale bar ``fraction surviving''.
(5) For the tree figure, the logo plot for that site is now shown in panel (A) of the same figure. So you can get rid of that, and just include labels that indicate that green means binding / neutralization by C179, and the letters are the amino acid at site 38.
}
}
\end{figure}
